Figure 1c

### 2017-11-21 inst/tcga_correlation/tcga_correlation.Rmd
re-ran tcga correaltion rmd

#save to pdf
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
pdf(path, width = 28)
data %>%
  arrange(cancer_PAM50, TP53, RP3) %>%
  plotTCGAcorrelation(type = "diploid only")
dev.off()

>>>>

#save to pdf
# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
# pdf(path, width = 28)
# data %>%
#   arrange(cancer_PAM50, TP53, RP3) %>%
#   plotTCGAcorrelation(type = "diploid only")
# dev.off()
